\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-07 doc/sw-system.tex
Added footnote to Terapix report, closes #163
Fixed SW paper refs

In this paper, we describe the \SW project, a web-based system conceived to
address the visual inspection problem in gravitational lens detection for future
large surveys by ``crowd-sourcing'' it to a community of citizen scientists.
Implemented as a Zooniverse \citep{SimpsonEtal2014}
project, it is designed to provide a {\it gravitational lens discovery service}
to survey teams looking for lenses in wide field imaging data. In a companion
paper \citep[][hereafter \PaperTwo](PaperII) we will present the new
gravitational lenses discovered in our first lens search, and
begin to investigate the differences between lens detections made in \SW and
those made with automated techniques. Here though, we simply try to answer the
following questions:

@@

The four CFHT Legacy Survey\footnote{\texttt{http://www.cfht.hawaii.edu/Science/CFHTLS/}}
\citep[\cfhtls,][]{Gwyn2012} ``Wide'' fields cover a total of approximately
160 square degrees of sky (after taking into account tile overlaps).
With high and homogeneous image quality (the mean seeing in the $g$-band is
0.78''), and reaching limiting magnitudes of around 25 across the $ugriz$ filter
set, this survey has yielded several dozen new gravitational lenses on both
galaxy and group scales
\citep{GavazziEtal2014,SonnenfeldEtal13,CabanacEtal2007,MoreEtal2012}. The
quality of the data, combined with the presence of these comparison ``known
lens'' samples, makes this a natural choice against which to develop and test
the \SW system. The \cfhtls is also well-representative of the data quality
expected from several next-generation sky surveys, such as DES, KiDS, HSC and
LSST.

>>>>

In this paper, we describe the \SW project, a web-based system conceived to
address the visual inspection problem in gravitational lens detection for future
large surveys by ``crowd-sourcing'' it to a community of citizen scientists.
Implemented as a Zooniverse \citep{SimpsonEtal2014}
project, it is designed to provide a {\it gravitational lens discovery service}
to survey teams looking for lenses in wide field imaging data. In a companion
paper \citep[][hereafter \PaperTwo]{MoreEtal2015} we will present the new
gravitational lenses discovered in our first lens search, and
begin to investigate the differences between lens detections made in \SW and
those made with automated techniques. Here though, we simply try to answer the
following questions:

@@

The four CFHT Legacy Survey\footnote{\texttt{http://www.cfht.hawaii.edu/Science/CFHTLS/}}
\citep[\cfhtls,][]{Gwyn2012} ``Wide'' fields cover a total of approximately
160 square degrees of sky (after taking into account tile overlaps).
With high and homogeneous image quality (the mean seeing in the $g$-band is
0.78''), and reaching limiting magnitudes of around 25 across the $ugriz$ filter
set, this survey has yielded several dozen new gravitational lenses on both
galaxy and group scales
\citep{GavazziEtal2014,SonnenfeldEtal13,CabanacEtal2007,MoreEtal2012}. The
quality of the data, combined with the presence of these comparison ``known
lens'' samples, makes this a natural choice against which to develop and test
the \SW system. The \cfhtls is also well-representative of the data quality
expected from several next-generation sky surveys, such as DES, KiDS, HSC and
LSST. We use the stacked images
from the final T0007 release taken from the Terapix
website\footnote{\texttt{http://terapix.iap.fr/cplt/T0007/doc/T0007-doc.pdf}} for this
work.
